RAX:Efficiently Evaluating the Complexity of Porting for RISC-V

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al. have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
To overcome these challenges, we propose RAX, an effective porting
complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
\begin{itemize}
  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
\end{itemize}
% The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors. Section 3 presents the implementation and evaluation of RAX. Section 4 and 5 presents related work and conclusions.

% \section{RAX}
% The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
% During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
% A scanning tool is built to get potential modification workload.
% Finally,an appropriate machine learning model is selected as a classification.
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure1.pdf}
%   \caption{Flow chart for method to build RAX}
%   \label{fig:figure1}
%   \Description{Flow chart for method to build RAX}
% \end{figure}
\section{Motivation}
We propose the following research questions:

@@

\textbf{RQ 2:} How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure2.pdf}
%   \caption{The relationship between score and CC}
%   \label{fig:figure2}
%   \Description{The relationship between score and CC}
% \end{figure}

To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
First,we try to use code complexity metrics to evaluate porting work.
The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code. Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The relationship between score and CC}
  \label{fig:figure2}
  \Description{The relationship between score and CC}
\end{figure}
\subsection{Factor 1: Cyclomatic Complex(CC)}
\label{sec:factor-1}
We use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
this section calculate the correlation coefficient using the Spearman Rank.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 projects adapted for RISC-V,collected from the OpenEuler list\citep{stage2023} and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0,5]$.
The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, the relationship of factors shown in Figure \ref{fig:figure2}.

>>>>

Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al. have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
To overcome these challenges, we propose RAX, an effective porting
complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
\begin{itemize}
  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
\end{itemize}
The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors. Section 3 presents the implementation and evaluation of RAX. Section 4 and 5 presents related work and conclusions.

% \section{RAX}
% The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
% During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
% A scanning tool is built to get potential modification workload.
% Finally,an appropriate machine learning model is selected as a classification.
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure1.pdf}
%   \caption{Flow chart for method to build RAX}
%   \label{fig:figure1}
%   \Description{Flow chart for method to build RAX}
% \end{figure}
\section{Motivation}
To help developers more accurately assess the porting complexity of C/C++ projects, we aim to answer the following research questions:

@@

\textbf{RQ 2:} How to implement fine-grained and automated tools to help developers accurately assess the complexity of their projects in real world?\\
As we all known, the metrics of projects porting complexity is influenced by many factors, such as the scale of projects,the logical structure of the architectural code. To answer RQ 1, we introduce the code Cyclomatic Complexity(CC) and Arch\_code.
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure2.pdf}
%   \caption{The relationship between score and CC}
%   \label{fig:figure2}
%   \Description{The relationship between score and CC}
% \end{figure}

% To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
% First,we try to use code complexity metrics to evaluate porting work.
% The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
% During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
% This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code. Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The relationship between score and CC}
  \label{fig:figure2}
  \Description{The relationship between score and CC}
\end{figure}
\subsection{Factor 1: Cyclomatic Complex(CC)}
\label{sec:factor-1}
First,we try to use code complexity metrics to evaluate porting work.
CC can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential porting difficulties,code complexity metrics helps the tool improve accuracy \cite{2005Exploring}.At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
Based on the above, we use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
this section calculate the correlation coefficient using the Spearman Rank.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 projects adapted for RISC-V,collected from the OpenEuler list\citep{stage2023} and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0,5]$.
The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, the relationship of factors shown in Figure \ref{fig:figure2}.
